Symbolic On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-02 main.tex
minor tweak

    To obtain the desired bisimulation \({∼}\) between \(\norm(⟨s⟩)\) and \(\norm(⟨u⟩)\), we add the pair \((s, t)\) to \(∼'\), 
    \[{∼} ≜ {∼'} ∪ \{(s, u)\},\] 
    with the following transition \(δ_{∼}\): for all \(α ∈ \At\),
    \begin{itemize}[nosep]
        \item If \(δ_{\norm(S)}(s, α) = δ_{\norm(U)}(u, α) = \accept\), then \(δ_{∼}((s, u), α) ≜ \accept\);
        \item If \(δ_{\norm(S)}(s, α) = δ_{\norm(U)}(u, α) = \reject\), then \(δ_{∼}((s, u), α) ≜ \reject\);
        \item If \(δ_{\norm(S)}(s, α) = (s', p)\) and \(δ_{\norm(U)}(u, α) = (u', p)\), then \(δ_{∼}((s, u), α) = ((s', u'), p)\)
        \item Finally, for all \((s', u') ∈ {∼}'\) that is not equal to \((s, u)\), we let \(δ_∼\) inherits the transition of \(δ_{∼'}\), i.e. \(δ_{∼}((s', u'), α) = δ_{∼'}((s', u'), α)\)
    \end{itemize}
    By checking all the requirement for bisimulation, we can verify that \emph{if \(δ_{∼}\) is well-defined}, then \(∼\) is indeed a bisimulation between \(\norm(⟨s⟩)\) and \(\norm(⟨u⟩)\).

@@

        Then by condition~\labelcref{itm:transition-bisim}, there exists a bisimulation \(∼_{s', t'}\) between \(⟨s'⟩\) and \(⟨t'⟩\) s.t. \(s' ∼_{s', t'} t'\). Because bisimulation preserves liveness (\cref{thm:bisim-preserve-liveness}), \(s', t'\) has to be both dead or live. 
        Finally, because \(s'\) is live, therefore \(u'\) is also live, and we obtain the final case in the definition of \(δ_{∼}\): \(δ_{\norm(S)}(s, α) = (s', p)\) and \(δ_{\norm(U)}(u, α) = (u', p)\).
    \end{itemize}
\end{proof}

>>>>

    To obtain the desired bisimulation \({∼}\) between \(\norm(⟨s⟩)\) and \(\norm(⟨u⟩)\), we add the pair \((s, t)\) to \(∼'\), 
    \[{∼} ≜ {∼'} ∪ \{(s, u)\},\] 
    with the following transition \(δ_{∼}\): for all \(α ∈ \At\),
    \begin{itemize}[nosep]
        \item If \(δ_{\norm(S)}(s, α) = δ_{\norm(U)}(u, α) = \accept\), then \(δ_{∼}((s, u), α) ≜ \accept\);
        \item If \(δ_{\norm(S)}(s, α) = δ_{\norm(U)}(u, α) = \reject\), then \(δ_{∼}((s, u), α) ≜ \reject\);
        \item If \(δ_{\norm(S)}(s, α) = (s', p)\) and \(δ_{\norm(U)}(u, α) = (u', p)\), then \(δ_{∼}((s, u), α) = ((s', u'), p)\)
        \item Finally, for all \((s', u') ∈ {∼}'\) that is not equal to \((s, u)\), we let \(δ_∼\) inherits the transition of \(δ_{∼'}\), i.e. \(δ_{∼}((s', u'), α) = δ_{∼'}((s', u'), α)\)
    \end{itemize}
    By checking all the requirement for bisimulation, we can verify that \emph{if \(δ_{∼}\) is well-defined}, then \(∼\) is indeed a bisimulation between \(\norm(⟨s⟩)\) and \(\norm(⟨u⟩)\) and \(s ∼ u\).

@@

        Then by condition~\labelcref{itm:transition-bisim}, there exists a bisimulation \(∼_{s', t'}\) between \(⟨s'⟩\) and \(⟨t'⟩\) s.t. \(s' ∼_{s', t'} t'\). Because bisimulation preserves liveness (\cref{thm:bisim-preserve-liveness}), \(s', t'\) has to be both dead or live. 
        Finally, because \(s'\) is live, therefore \(u'\) is also live, and we obtain the final case in the definition of \(δ_{∼}\): \(δ_{\norm(S)}(s, α) = (s', p)\) and \(δ_{\norm(U)}(u, α) = (u', p)\).
        \qedhere
    \end{itemize}
\end{proof}
